---
title: "Econ Proj"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(startupmsg)
library(distr) 
library(ggplot2)
library(crayon)
library(extraDistr)
library(VGAM)
library(dplyr)
library(ltm)
dataset=read.csv("/Users/wayne/Desktop/compiled_dataset_04_24.csv")
```


```{r}
df=dplyr::select(dataset, field, scope, citations )
df
```

```{r}
muscope=sum(df$scope=="yes")/length(df$scope)
alt=(df$scope=="yes") 
df$scope=alt
df$scope <- as.numeric(df$scope)
```
Observable correlation? Is there anyway we can safely estimate how the citation count relates to in/out of scope?
Since it is a boolean variable for in/out of scope, I used point biserial correlation.
```{r}
dftest=dplyr::select(df, field, citations )
```
```{r}
aov(scope~citations,data=df)
```

```{r}
df[is.na(df)] <- 0
cor(df$scope,df$citations)
```
The citation count and in/out of scope has a rather weak correlation.
The magnitude result does not strongly affect the reputation/academic notability in Econ field. However, it does suggest a weak correlation. 
```{r}
ggplot(df, aes(x=df$field, y=(df$citations)/(sum(df$citations))))+geom_bar(stat = "identity")+labs(
        x = "Field",
        y = "Percentage of Citation")
```
```{r}
devdf=filter(df, field=="Dev")
cor(devdf$scope, devdf$citations)
```
```{r}
findf=filter(df, field=="Fin")
cor(findf$scope, findf$citations)
```
```{r}
intldf=filter(df, field=="Intl")
cor(intldf$scope, intldf$citations)
```
```{r}
iodf=filter(df, field=="IO")
cor(iodf$scope, iodf$citations)
```
```{r}
labdf=filter(df, field=="Labor")
cor(labdf$scope, labdf$citations)
```
```{r}
lawdf=filter(df, field=="Law")
cor(lawdf$scope, lawdf$citations)
```
```{r}
macdf=filter(df, field=="Macro")
cor(macdf$scope, macdf$citations)
```
```{r}
pubdf=filter(df, field=="Public")
cor(pubdf$scope, pubdf$citations)
```
```{r}
datatest=data.frame(df %>% group_by(df$field) %>% tally())
datatest
```
```{r}
data_group <- dftest %>%                                 # Group data
  group_by(field) %>%
  dplyr::summarize(gr_sum = sum(citations)) %>% 
  as.data.frame()
data_group               
```
```{r}
test<-lm(gr_sum~field,data=data_group)
anova(test)
```


```{r}
library(coin)
t.test(macdf$citations,pubdf$citations)
```
```{r}
data1=filter(dftest, field!="Fin")
data1=filter(data1, field != "IO")
kruskal.test(citations~field, data1)
```

